Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-23 WSSSPE2_report/WSSSPE2_review.tex
Section 3.2: Minor changes.

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Neil Chue Hong, We are the 92$\%$} 
\label{keynote2}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

In a recent survey of UK research-intensive universities, 92\% of researchers
said they used research software and 68\% said their research would be impossible
without software. Yet 71\% have had no formal software training, and few are
ready to apply many of the things we take for granted such as testing or
virtualization. WSSSPE represents the pinnacle of what we understand to be the
best practice around scientific software in our community. My talk will
challenge the workshop participants to come up with ways of taking this best
practice to those 92\% of researchers in a way that will lead to maximum benefit
to the scientific community.

@@

Where indicated slides licensed under World-leading research relies on software

@@

Software is not special it is mainstream software?

@@

And 	attitudes 	are	changing

Overall

 which 	is	changing 	the	situation

PhD students

@@

The cost of UK research that relies on software is 
£840m!

Investment in 2013--2014 financial year, an amount that has risen by
3\% on average over last four years

30\%

Of total research investment has been spent on research which relies on software
over the last four financial years

@@

We	can 	talk	all	day 	about 	the best 	ways	of	achieving sustainability

But	what	are	we	going 	to	do to	make	it	actually sustainable?

Careers outside academic sector

Non-university Research (industry, government etc.)

UK	STEM graduate career paths

Early Career
Research

Permanent
Research Staff

Professor

@@

Who	are	the	people 	we	need to	persuade?

What		are	the	incentives 	we need 	to	put 	in	place?

How are we going to show that the work we present here has benefit to the 92\%?

>>>>

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Neil Chue Hong, We are the 92$\%$} 
\label{keynote2}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{comment}
In a recent survey of UK research-intensive universities, 92\% of researchers
said they used research software and 68\% said their research would be impossible
without software. Yet 71\% have had no formal software training, and few are
ready to apply many of the things we take for granted such as testing or
virtualization. WSSSPE represents the pinnacle of what we understand to be the
best practice around scientific software in our community. My talk will
challenge the workshop participants to come up with ways of taking this best
practice to those 92\% of researchers in a way that will lead to maximum benefit
to the scientific community.
 \end{comment}

@@

World-leading research relies on software

@@

Software is not special; it is mainstream software

@@

And 	attitudes 	are	changing, which 	is	changing 	the	situation

@@

The cost of UK research that relies on software

\textsterling 840 million of investment in 2013--2014 financial year, an amount that has risen by
3\% on average over last four years

30\% Of total research investment has been spent on research which relies on software
over the last four financial years

@@

We	can 	talk	all	day 	about 	the best 	ways	of	achieving sustainability
But	what	are	we	going 	to	do to	make	it	actually sustainable?

Careers outside academic sector: 
Non-university Research (industry, government, etc.)

UK STEM graduate career paths: Early Career Research, Permanent Research Staff,
Professor

@@

Who	are	the	people 	we	need to	persuade?
What		are	the	incentives 	we need 	to	put 	in	place?
How are we going to show that the work we present here has benefit to the 92\%?
